\section{The GUM}
The Guide to the Expression of Uncertainty in Measurement (GUM) is our basic guidance document for the calculation of measurement uncertainty. 

The current GUM edition was released in 2008 and is the first edition published by the BIPM JCGM. It has very minor corrections to earlier ISO editions published in 1995 and 1993. 

Previous editions had to be purchased from the ISO, but the GUM is now available free of charge. A PDF copy can be downloaded:
\begin{quote}
\url{http://www.bipm.org/utils/common/documents/jcgm/JCGM_100_2008_E.pdf}
\end{quote}
and an HTML version is available:
\begin{quote}
\url{http://www.iso.org/sites/JCGM/GUM/JCGM100/C045315e-html/C045315e.html?csnumber=50461}
\end{quote}

A suitable bibliographic reference (taken from Metrologia) is: 
\begin{quote}
BIPM, IEC, IFCC, ISO, IUPAC, IUPAP and OIML 2008,\textit{``Evaluation of Measurement Data—Guide to the Expression of Uncertainty in Measurement JCGM 100:2008 (GUM 1995 with minor corrections)''}, 1st edition (S\`evres: BIPM Joint Committee for Guides in Metrology). 
\end{quote}

\paragraph{GUM reference for calibration reports}
the following phrase is sufficient
\begin{quote}
See the \textit{``Guide to the expression of uncertainty in measurement JCGM 100:2008''} (BIPM, 1st edition, 2008) for an explanation of terms.
\end{quote}
(While the title is incomplete, using either the text in parentheses or the quoted text in a Google search returns a link to the on-line versions immediately.)

\subsection{GUM Supplements}
Two GUM Supplements have also been released: GUM Supplement 1 (S1)~\cite{GUM_S1} and GUM Supplement 2(S2)~\cite{GUM_S2}. Use of S1, and the second part of S2 that deals with Monte Carlo methods, is not recommended until serious issues have been resolved relating to the meaning of probability in uncertainty statements \cite{WHITE_16}. The interpretation of probability used in the supplements is Bayesian and has not been tied to the unpredictable behaviour of measurement errors in experiments. For this reason, a physically meaningful interpretation cannot be given to uncertainty statements obtained from using the supplement Monte Carlo methods. 

\subsubsection{Multidimensional measurands}
GUM Supplement 2 addresses the evaluation of measurement uncertainty for multidimensional measurands, which is not covered in the GUM or S1. The first part of S2 describes extensions to the analytical techniques described in the GUM. These extensions are compatible with the conventional interpretation of probability, as a ``relative frequency of events'', and so they may be used. A more extensive review of multidimensional extensions to the GUM has been published \cite{HALL_15}.

