\section{Copyright and licensing}
 \label{s_copyright}
Copyright is a property right that exists in certain original works. With few exceptions, copyright exists in original works created by government agencies. A licence (that is, permission) is needed to reuse most government copyright works because, without one, a person will infringe copyright in a work when he or she does any of a number of ``restricted acts''. The most common restricted act is copying the work or a substantial part of it.

Creative Commons licences are freely available copyright licences that enable the reuse of copyright works in a standardised way. Creative Commons is an international organisation with affiliate organisations around the world. Information about the New Zealand affiliate organisation can be found at \cite{CCNZ}. 

The New Zealand Government Open Access and Licensing framework (NZGOAL) \cite{NZGOAL} provides guidance for government agencies to follow when releasing copyright works and non-copyright material for re-use by others. NZGOAL seeks to foster a culture of sharing of government material and encourages the licensing of government copyright works for re-use using Creative Commons New Zealand law.
 
\proposedbox{
A Creative Commons (CC) licence is likely to be appropriate for MSL's own publications. Two types of CC licence cover basic needs. There is a licence called ``Attribution-NoDerivatives 4.0 International'' (CC BY-ND 4.0), which allows re-users to copy and distribute the material in any medium or format, including for commercial purposes. However, modifications to the work are not permitted, nor is it permitted in any way to suggest that the licensor endorses the use of the material. The CC BY-ND 4.0 licence is recommended for MSL Technical Guides. 

The other type of CC licence that may be appropriate for MSL  publications is called ``Attribution 4.0 International'' (CC BY 4.0). This license requires that re-users give credit to the creator. Re-users may distribute, remix, adapt, and build upon the material in any medium or format, even for commercial purposes. The CC BY 4.0 licence is used by some scientific journals. This licence may be more appropriate  than the CC BY-ND 4.0 licence for MSL's Technical Reports.

There is an add-on for Microsoft Office which can insert CC licences in Word documents (unfortunately, the spelling of ``licence'' is American). The \LaTeX\ templates for Technical Guides and Technical Reports include Creative Commons licences.
}

